---
title: "Markdown"
author: "Isabelle Smith"
date: "2025-01-21"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Test text: blah blah blah.

Two returns for new paragraph.

First line.
(Two spaces...) Second line.

# Biggest Header

## Second Header




### (Multiple Returns...) Third Header

Use one set of asterisks for *italic text* and two sets for **bold text**. Use carets for ^superscript^ and tildes for ~subscript~. Two tildes makes ~~strikethrough~~.

- list item  
- (two spaces...) list item
  + indented list item


wow! a [link](www.google.com)!

Table | with | text
------|------|-----
lots  | of   | text
so    | many | rows


#### Fencing:

For `in-line` use a single tick mark, and for  

```
centered
```

use three.


#### In-Line Code:

Insert a calculation and only show output: `r 7 + pi`

#### Code Chunks

```{r}

7 + pi

```


Adding `{r eval=TRUE, echo=FALSE}`:

```{r eval=TRUE, echo=FALSE}

7 + pi

```


#### LaTeX

Single dollar signs: $a+b=c$

Double dollar signs: (new line)

$$a+b=c$$

